Pteropod physiological analysis

### 2018-03-09 physio.Rmd
rda loadings to biplot, adding ty2, ty3, scarring to physio

envchr <- c('pCO2', 'pH', 'CO3', 'Ara', 'O2', 'Temp', 'Fluor')
ptechr <- c('abu', 'dis', 'len')
```

@@

@@

>>>>

envchr <- c('pCO2', 'pH', 'CO3', 'Ara', 'O2', 'Temp', 'Fluor')
ptechr <- c('abu', 'dis', 'len', 'ty2', 'ty3', 'scr')
```

@@

RDA axis loadings
```{r}
summary(mod)$biplot %>% round(2) %>% kable
```

@@

## type 2 dissolution
```{r}
knitr::kable(filter(mods, pte_lab %in% 'ty2'), caption = 'ty2')
```

## type 3 dissolution
```{r}
knitr::kable(filter(mods, pte_lab %in% 'ty3'), caption = 'ty3')
```

## scarring
```{r}
knitr::kable(filter(mods, pte_lab %in% 'scr'), caption = 'scr')
```
